I would first like to thank my adviser Prof. Raj Nadakuditi. Thank you for allowing me to
be one of your very first students. Your ideas and passion for research truly do
inspire. Thank you for teaching me how to pick the low hanging fruit, how to see the
strucutre in complicated problems, and how to always ``push it through''.

I would specifically like to thank my committee members for their inspiring conversations
and courses over the past 5 years. Prof. Rada Mihalcea, thank you for your information
retrieval course. I enjoyed chatting with you about the possible applications of
correlation analysis to such problems. Prof. Laura Balzano, thank you for coming to the
University of Michigan; I consider myself lucky that your arrival was timed so perfectly
with my dissertation. You have been a wonderful addition to EE:S and I am excited to learn
from your work in the years to come. Prof. Alfred Hero, thank you for our numerous
conversations over the years at conferences and MURI funding meetings. Your insights
always helped to deepen my understanding of the problems that we solve. I would also like
to thank my undergraduate research advisers at the University of Maryland, Prof. Jonathan
Simon and Prof. Adam Hsieh, for first introducing me to the research process.

Thank you to all the members of the Nadakuditi group - Curtis Jin, Raj Tejas Suryaprakash,
Himanshu Nayar, Brian Moore, Arvind Prasadan, and David Hiskens. Specifically, I would
like to thank Raj Tejas for his help with the analysis of missing data and Brian Moore for
his wonderfully elegant hacks of \textsc{MATLAB}.

Thank you to all the members of the Graduate Student Council and SPeecs organizing
committee. Specifically I would like to thank Kevin Xu, Michael Allison, and Mads
Almassalkhi for their leadership and passing down the needed graduate student lore. Thank
you also to the advanced technology group at 3M. I thoroughly enjoyed my internship last
summer and am looking forward to working with you all over the next years. I would also
like to thank the National Basketball Association for providing an escape from research. 

To my high school friends Alex McArthur, John Vaccacio, Allison Seyler, Andy Mellon, Matt
Keel, Alec Brown, Chris Rowe, Mike Hyle, and Jason Pribble: thank you for always being
there to remind me of my roots. While I have only sporadically been able to spend time
with you in person over the last five years, I valued every minute of it. Alex - thank you
for teaching me to always trust your decisions. Allison, Alec, Andy, Chris and Jason -
thank you for humoring me by listening to my academic ramblings. Matt, Mike, and John
- thank you for always keeping me guessing. 

To my friends from the University of Maryland, Jaime Gomez, Austin Myers, Sarah Saslow,
Kyle Smith, Andy Peters, and Nick Gagliolo: thank you for always being there and for
appreciating the alma mater as much as I do - ``steadfast in loyalty''. Jaime - I will
never forget all of the memories at Courtyards. Thank you for teaching me how to play
tennis, bridge, and spades. Thank you for teaching me about nuclear physics and for
always providing logical advice when I needed it.  Sarah - thank you for always providing
a listening ear when I needed it. Thank you for all of the football weekends as we watched
Michigan and Northwestern in graduate school. Kyle - thank you for all of the late night
card games and video games, for teaching me about fire protection engineering, and all of
the weekends that we were able to see each other since graduation. Austin - thank you for
being an awesome roomate and colleague, for your goofy sense of humor,
and all of the conversations that we had. Nick - thank you for keeping me sane through all
of the courses, group projects, exams, and gemstone activities. Andy - thank you for all
of the sports conversations and going to all of the Maryland games with me over the years.

To my friends and colleagues at the University of Michigan, Rob Vandermeulen, Madison
McGaffin, Mitchell Thomas Hellman Young, Matthew Prelee, Steve Schmitt, Paul Ozog, Eric
Uthoff, Pat O'Keefe, and Mike Henry: thank you for making graduate school fun. Paul, Eric,
and Pat - thank you for all the first and second year hang outs that got us through our
coursework. Steve - thank you for all the walk-and-talks, letting me borrow your sitting
ball, and teaching me about the midwest. Rob - thank you for introducing me to your many
hobbies; you have really broadened my world view. Matt - thank you for all of the
walk-and-talks, football trips, sports arguments, board game nights, and long runs. Mike -
thank you for being really good at trivia and the many fun nights at your place. Mitch -
thank you for teaching me how to brew, being a Linux whisperer, teaching me about flux,
and for the HoM. Madison - thank you for all of the walk-and-talks, entertaining my OCD
Pathfinder ideas, teaching me how to make bread, being a word-o-mancer, and all of the
memories contained at HoM.

To my girlfriend Christie VanTongeren - thank you for all of your support over the past
three years. Thank you for your understanding for all of the late nights over the past
months and always listening. Thank you teaching me all of your expert cooking
techniques and for all of the movie, bowling, game, and trivia nights. Thank you
for sharing my values but always challenging me to be better. I am so excited for
Minneapolis.

I would like to thank all of the EECS support staff who made my job easier over the years
at the University of Michigan. Special thanks go to our graduate coordinators Becky
Turanski, Beth Stalnaker, and Rachel Young Antoun. Thank you for always being there to
answer questions, keeping me on track, and brightening up my day. Thank you also to our wonderful
4th floor staff Beth Lawson, Anne Pace, and Shelly Feldkamp. You make our jobs so
easy by hiding the many  complicated intricacies of the funding process. I also
greatly appreciated your kindness and support over the last four years. It was always a
pleasure to catch up with you.

I would like to thank my piano teacher of eight years, Shirley Elsroad, and organ teacher Lee
Pogue. Thank you for teaching the joy of the piano and organ and teaching me to express
myself though them in my own voice. I will always fondly remember my lessons with the both
of you. I would also like to thank Prof. Steven Ball for teaching me how to play the
carillons at the University of Michigan. Thank you for teaching me how to perfume the Ann
Arbor air with music.

Finally, I would like to thank my mother Nancy, father David, and sister Amy. I
would not be where I am today without your support, encouragement, and amazing
parenting. I know that not everyone is as lucky as I was to be born into such a supportive
enviornment and for that, words cannot describe my gratitude. This thesis is a testament
to your parenting skills. 
