\documentclass[11pt]{article}
\usepackage{times,geometry,algorithm,algorithmic,amsmath,amssymb,amstext,color}
\geometry{letterpaper, tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}
\title{Proof Edits}
\author{Nicholas Asendorf and Raj Rao Nadakuditi}
\date{T-SP-13946-2012 - IEEE Transactions on Signal Processing - ``The Performance of a Matched Subspace Detector that Uses Subspaces Estimated from Finite, Noisy, Training Data"}

\input{IEEE_RMT_MSD_header.tex}

\begin{document}
\maketitle

\noindent{To whom it may concern,}

Could you please make the following changes to the proof
\begin{itemize}
  \item Please replace ``an'' in the title with ``a''. It should read ``The Performance of
    a Matched Subspace Detector That Uses Subspaces Estimated From Finite, Noisy, Training
    Data''.
  \item Page 1, Introduction, Third paragraph. The second reference to [13] should read
    ``[13, Table 10.1, pp. 121],''. Please delete the extra brackets and place the comma
    on the outside of bracket.
  \item Page 2, Figure 1, If the labels ``Stochastic setting'' and ``Deterministic
    setting'' cannot be placed directly under each subfigure, please remove them from
    the last line of the caption.
  \item Page 2, Figure 2. The reference to equation (19) in the caption should reference
    equation (13).
  \item Page 3, Section II.A, can ``$\sigma_1>\sigma_2>\dots>\sigma_k>0$'' all be on one
    line?
  \item Page 3, Section II.B, please place both equation lines of equation (1) in the same
    column. i.e. please don't split $\widehat{U}$ and $\widehat{\sigma}_i^2$ in different
    columns.
  \item Page 4 - Can the equation labels for (7), (8), (10), and (12) be vertically centered with
    their respective boxed equation? They are all a little low.
  \item Page 5, Section IV.A - Can the two lines of the indented statement ``Design a new
    detector...subspace estimation accuracy.'' please be left aligned to eachother (but
    still indented from the normal paragraph). Currently the first line is extra indented.
  \item Page 5, first paragraph in second column starting with ``The detector
    derivations...'' - This is a continuation of the previous paragraph. Please delete the
    indentation.
  \item Page 6 - Please vertically center the equation label (16) with the boxed
    equation. It is a little low.
  \item Page 6, There is a ``1)'' immediately before the Claim 5.1. Please remove ``1)''.
  \item Page 7, equation (18) - Can the split of the equation happen after the ``and'' so
    that the second line of the equation is ``$\widehat{w}|H_1\sim\mathcal{N}...$''. Can
    the two lines then be horizontally centered?
  \item Page 7, Please vertically center the equation label (20) with the boxed
    equation. It is a little low.
  \item Page 7, Section VI.B, the equation ``$\Lambda(\widehat{w})...$''. Can you please make
    this equation fit on one line by doing the following: Place
    ``$\Lambda(\widehat{w})=$'' inline immediately after ``becomes'', so it reads
    ``becomes $\Lambda(\widehat{w})=$''. The remaining equation should fit on one
    line. Please remove the $\times$ that was added to the equation at the point at which    
    it was split up.
  \item Page 8, first column, first equation beginning with
    ``$\Lambda(\widehat{w})$''. Please remove the $\times$ in the middle of this equation.
  \item Page 8, equation (22). Please don't split the two lines of equation (22) across
    columns. Please have the $P_F$ and $P_D$ immediately following one another.
  \item Page 8, equation (23). Please split this equation after the comma and
    horizontally align the equations so it looks like.
    \begin{equation*}
      \begin{aligned}
        & \Lambda(\widehat{w})|H_0\sim\sum_{i=1}^{\widehat{k}}d_i\chi_{1i}^2,\\
        & \Lambda(\widehat{w})|H_1\sim\sum_{i=1}^{\widehat{k}}d_i\left(\sigma_i^2|\langle
          u_i, \widehat{u}_i\rangle|^2 +1\right)\chi_{1i}^2\\
      \end{aligned}
    \end{equation*}
  \item Page 9, equation (26). Can both lines of the equation be horizontally centered?
  \item Page 9, section VIII.B, second column, first paragraph. The phrase ``plot three
    empirical ROC curves for $n=50 200 1000$'' should read ``plot three
    empirical ROC curves for $n=50, 200, 1000$''. Please add the commas between the
    numbers.
  \item Page 10, Figure 3, caption. Please remove ``(a) $k=2,c=1$ (b) $k=4,c=10$'' from
    the last line of the caption.
  \item Page 10, Figure 4, The reference to equation (22) should be equation(16).
  \item Page 10, Figure 4, caption. Please remove ``(a) Stochastic (b) Deterministic''
    from the last line of the caption.
  \item Page 11, Figure 5, caption. Please remove ``(a) $m=5000$ (b)$m=250$ ''
    from the last line of the caption.
  \item Page 11, first full paragraph of first column. The sentence ``Fig. 5 chooses
    $20m=n$ so that $c=20$...'' should begin ``Fig. 5(b)...''.
  \item Page 11, Figure 6, caption. The reference to (19) should be (13).
  \item Page 11, Figure 6, caption. Please remove ``(a) Stochastic (b) Deterministic ''
    from the last line of the caption.
  \item Page 12, Section IX, second paragraph. The sentence ``In setting where a
    practitioner might play-it-safe and set $\widehat{k}>\widehat{k}_{\text{eff}}$, the
    performance loss in significant'' should read ``In setting where a
    practitioner might play-it-safe and set $\widehat{k}>\widehat{k}_{\text{eff}}$, the
    performance loss is significant''. Replace ``in'' with ``is'' in the second to last word. 
  \item Page 13, equation (27). There are two dots after this equation. There should only
    be one period. The equation label is also low.
  \item Page 13, equation (28). There are two dots after this equation. There should only
    be one period. The equation number is also low.
  \item Page 13, equation (30). Can you please make the break before the diag so that
    $M_n\left(\widehat{\lambda}_i\right)\convas$ is on the first line, leaving
    $\diag\left(...\right)$ on the second line?
  \item Page 13, second column, second to last sentence. Please change ``...and the
    smallest gap between $k$ successive eigenvalues is at least as large as ...'' to
    ``...and the largest gap between $k$ successive eigenvalues is at most
    $O\left(...\right)$''. Please replace ``smallest'' with ``largest'' and ``least as large as'' with ``most''
  \item Page 14, Reference [11] new bibtex entry:\\
    @inproceedings\{mcwhorter2003matched,
  title=\{Matched subspace detectors for stochastic signals\},
  author=\{McWhorter, L. T.  and Scharf, L. L.\},
  booktitle=\{Proc. 11th Ann. Workshop on Adaptive Sensor Array Process. (ASAP)\},
  year=\{2003\},
  organization=\{Lexington, MA, Mar. 11-13\}
\}
  \item Page 14, Reference [20] new bibtex entry:\\
@article\{benaych2011eigenvalues,
  title=\{The eigenvalues and eigenvectors of finite, low rank perturbations of large random matrices\},
  author=\{Benaych-Georges, Florent and Nadakuditi, Raj Rao\},
  journal=\{Advances in Mathematics\},
  volume=\{227\},
  number=\{1\},
  pages=\{494--521\},
  year=\{2011\},
  publisher=\{Elsevier\}
\}
  \item Page 14, Reference [22] new bibtex entry:\\
@inproceedings\{asendorf2011improving,
  title=\{Improving and characterizing the performance of stochastic matched subspace detectors when using noisy estimated subspaces\},
  author=\{Asendorf, Nicholas and Nadakuditi, Raj Rao\},
  booktitle=\{Signals, Systems and Computers (ASILOMAR), 2011 Conference Record of the Forty Fifth Asilomar Conference on\},
  pages=\{1893--1897\},
  year=\{2011\},
  organization=\{IEEE\}
\}
\end{itemize}


Thank you very much. Please do not hesitate to email or call me directly at
asendorf@umich.edu or 443-605-3018.

\noindent{Sincerely,}

The authors












\end{document}
